\documentclass{My_CV}



%---------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%  CV Starts Here  %%%%%%%%%%%%%%%%%%%%%



\begin{document}



\justifying



%%%---------------------Column Style---------------------%%%
\columnratio{0.34}
\setlength{\columnsep}{1cm}
\setlength{\columnseprule}{1.25mm}
\colseprulecolor{RosyBrown3}



\begin{paracol}{2}



%%%---------------------Left Column---------------------%%%
\begin{leftcolumn}
\backgroundcolor{c[0](6mm,6mm)}{Ivory2}



\vfill\null
%%%---------------------Contact---------------------%%%
\subsection{{\faTags} Contact}

\textcolor{Tan4}{\faEnvelope} : \href{mailto: priyalbordia111@gmail.com}{priyalbordia111@gmail.com} \\
\textcolor{SteelBlue1}{\faLinkedinSquare} : \href{https://www.linkedin.com/in/priyal-bordia-50026014a/}{Priyal Bordia} \\
{\faGithub} : \href{https://github.com/priyalbordia}{Priyal Bordia} \\
\textcolor{Purple3}{\faMobile} : (+91) 8141433029 \\
\textcolor{Coral2}{\faHome} : Aashirvad Avenue, VIP Road, Surat, Gujarat (395017)



\vfill\null
%%%---------------------Standardized Scores---------------------%%%
\subsection{{\faBookmark} Standardized Scores}

\cbfa{International English Language Testing System (IELTS):} \hfill{(2 January, 2022)} \\

\scalebox{0.8}{\smartdiagram[descriptive diagram]{{8.0,{Listening}}, {8.0,{Reading}}, {6.5,{Writing}}, {7.0,{Speaking}}, {\textbf{7.5},{\textbf{Overall Band Score}}}, {\textbf{C1},\textbf{{CEFR Level}}}}}



\newpage
%%%---------------------Skills---------------------%%%
\subsection{{\faCubes} Skills}

\setlength{\fboxrule}{3pt}
\fboxsep=7pt

\fcolorbox{Azure4}{LavenderBlush1}{Keynote}
\hspace{1mm}
\fcolorbox{Azure4}{Wheat1}{Pages}
\hspace{1mm}
\fcolorbox{Snow4}{LightSteelBlue1}{Numbers} \\
\hspace{1mm}
\fcolorbox{Snow4}{Honeydew1}{Google Workspace}
\hspace{1mm}
\fcolorbox{Snow4}{LightSalmon1}{iMovies} \\
\hspace{1mm}
\fcolorbox{Snow4}{LightCyan1}{Social Media Handling}
\hspace{1mm}
\fcolorbox{Snow4}{LemonChiffon1}{Canva} \\
\hspace{1mm}
\fcolorbox{Snow4}{Khaki2}{Science Outreach}
\hspace{1mm}
\fcolorbox{Snow4}{DarkOliveGreen1}{Vectornator} \\
\hspace{1mm}
\fcolorbox{Snow4}{Bisque1}{Sketchbook}



%%%---------------------Languages Spoken---------------------%%%
\subsection{{\faLanguage} Languages Spoken}

\scalebox{0.8}{\smartdiagram[priority descriptive diagram]{Spanish - Rudimentary, Prakrit - Rudimentary, Sanskrit - Rudimentary, Marathi - Good, Marwari - Good, Gujarati - Fluent, English - C1 Proficiency Level, Hindi - Native}}



\vfill\null
%%%---------------------Programming Languages---------------------%%%
\subsection{{\faLaptop} Programming Languages}

\cvskill{Python}{1.5}

\cvskill{SciLab}{1}

\cvskill{\LaTeX}{5}



\newpage
%%%---------------------Extra-Curricular Activities---------------------%%%
\subsection{{\faSmileO} Extra-Curricular Activities}

\cbfd{Art and Craft} \hfill{(Present)} \\
\cita{Sketching, Calligraphy, Paper Quilling, Make best use of waste} \\
Autodidact artist in all the above mentioned skills. \\

\cbfd{Classical Dance} \hfill{(13 August, 2011)} \\
\cita{Kathak} \\
1st year degree in Kathak.



\vfill\null
%%%---------------------Referees---------------------%%%
\subsection{{\faLeaf} Referees}

\cbfa{\scshape{Prof. Marina Cortês}} \\
\cita{Institute for Astrophysics and Space Sciences, University of Lisbon} \\
Email: \underline{mvcortes@fc.ul.pt} \\
    
\cbfa{\scshape{Dr Ravi Margasahayam}} \\
\cita{National Aeronautics and Space Administration (NASA)} \\
Email: \underline{rmargashayam50@icloud.com}



\end{leftcolumn}



%%%---------------------Right Column---------------------%%%
\begin{rightcolumn}



%%%---------------------Title---------------------%%%
\fcolorbox{Snow1}{Thistle3}{\begin{minipage}[c][2cm][c]{14cm}
	\begin {center}
		{\textcolor{Snow1}{{\textbf{\scshape{\Huge{Priyal Bordia — CV}}}}}} \\
		\textcolor{Snow1}{\rule[-1mm]{4cm}{1mm}} \vspace{-7mm} \\
	\end {center}
\end{minipage}} \\



%%%---------------------Research Profile---------------------%%%
\section{{\faFlask} Research Profile}

\begin{itemize}

    \item \cbfa{Circle of Life} \\
    \cita{Supervisor - Prof. Marina Cortês} \hfill{(21 September, 2021 - Present)}
    
    \item \cbfa{Gender Ratio Analysis} \\
    \cita{Supervisor - Prof. Prajval Shastri} \hfill{(10 August, 2021 - Present)}
    
    \item \cbfa{Rover Designing: “Titan Exploration Using Autonomous DroneBoat with Sample Analysis \& Visual Perspective”} \hfill{(February, 2021 - October, 2021)} \\
    
\end{itemize}

**Summarize from full CV after completion**



%%%---------------------Publications---------------------%%%
\section{{\faBook} Publications}

\begin{itemize}

    \item Prathmesh Barapatre, Rutuja Pilgar, \cbfd{Priyal Bordia}, \href{https://dl.iafastro.directory/event/IAC-2021/paper/66117/}{\textbf{“Titan Exploration Using Autonomous DroneBoat with Sample Analysis \& Visual Perspective”}}, \cita{International Astronautical Conference (IAC), Oct 24 – 29th. 2021, PAPERCODE - IAC-21, A3,5,8, x66117}
    
\end{itemize}



%%%---------------------Acknowledged---------------------%%%
\section{{\faConnectdevelop} Acknowledged}

\begin{itemize}

    \item Marina Cortês, Stuart A. Kauffman, Andrew R. Liddle, and Lee Smolin, \href{https://www.biocosmology.earth/s/Paper1-FINAL.pdf}{\textbf{“BioCosmology: Towards the Birth of a New Science”}}, \cita{arXiv:2204.09378 [astro-ph.CO]}
    
\end{itemize}



%%%---------------------Blogs---------------------%%%
\section{{\faNewspaperO} Blogs}

\begin{itemize}
    \item \href{https://nssmumbai.blogspot.com/2022/02/primordial-black-holes.html}{\textbf{“Primordial Black Holes”}} \\
    \cbfd{Priyal Bordia} \\
    \cita{National Space Society (USA)-Mumbai — NSS Mumbai Blog}
    
\end{itemize}



%%%---------------------Education---------------------%%%
\section{{\faGraduationCap} Education}

\begin{itemize}
    
    \item \cbfc{BSc. (Physics) — 7.66 GPA / Max. GPA 10} \\
    \cita{Ramnarain Ruia Autonomous College} \hfill{(July 2017 - October 2020)} \\
    \cita{Mumbai University}
    
    \item \cbfd{Grade 12 — 70\%} {(CBSE)} \\
    \cita{Radiant English Academy (Umra), Surat} \hfill{(March 2017)}
    
    \item \cbfd{Grade 10 — 8.0 CGPA / Max. CGPA 10} {(CBSE)} \\
    \cita{Radiant English Academy (Umra), Surat} \hfill{(March 2015)}

\end{itemize}



%%%---------------------Outreach Experience---------------------%%%
\section{{\faGroup} Outreach Experience}

\begin{itemize}
    \item \cbfa{National Space Society (USA) - Mumbai} \\
    A non-profit and educational organization, which is communicating STEM and space amongst enthusiasts through various activities. \\
    \cita{\cbfd{Mentors:} Dr. Ravi Margasahayam, Piyush Khopkar and Rachana Nath} \\
    
    \begin{itemize}
    
        \item \cita{Team Head} \hfill{(10 June, 2022 - Present)} \\
        \cbfd{Role:} Lead the Operations Team and PR Team.
        
        \item \cita{Public Representative Team Head} \hfill{(10 August, 2021 - 10 June, 2022)} \\
        \cbfd{Role:} Spokesperson of the organization, lead and manage the Public Representative Team.
        
        \item \cita{Public Representative} \hfill{(4 January - 9 August, 2021)}

    \end{itemize}
    
    \item \cbfa{Supernova Foundation: Mentoring for Women in Physics} — \textit{(Volunteering)} \\
    \cita{Social Media Team} \hfill{(February, 2021 - Present)} \\
    A non-profit mentoring program where women Physicists from around the globe have connected to mentor or seek mentoring from professionals.
    
    \item \cbfa{Vigyaan Samagam — Nehru Science Centre (Mumbai)} — \textit{(Volunteering)} \\
    \cita{Volunteer at CERN Stall} \hfill{(22 May - 29 May, 2019)} \\
    India’s first Mega Science Exhibition where India’s contribution in Mega Projects around the world was showcased. \\
    \cita{\cbfd{Supervisor:} Dr. Vikas Jain, Raja Ramanna Centre for Advanced Technology (RRCAT)} \\
    
\end{itemize}

My extreme passion for communicating science with the public led me to contribute in various Outreach Opportunities. At NSS Mumbai; a non-profit and educational organization, I am Team Head. I lead Operations and Public Relations Team, by supervising all the requirements of an event from inviting guests, promoting of event to smooth handling of it. With NSS Mumbai, I communicate STEM and space along with my team amongst enthusiasts through various activities like webinars, podcasts, etc. We keep these freely accessible for everyone. At Supernova Foundation; a non-profit program where women Physicists from around the globe have connected to mentor or seek mentoring for career as a Physicist. I handle its social media platforms and use these to promote women in Physics through various campaigns. At Vigyaan Samagam; India’s first Mega Science Exhibition. I communicated CERN’s Large Hadron Collider's (LHC) contribution to Particle Physics, Particle Astrophysics and technology and India’s contribution in LHC to visitors at the exhibition.



%%%---------------------Summer Schools and Workshops Attended---------------------%%%
\section{{\faHourglass[2]} Summer Schools and Workshops Attended}

\begin{itemize}

    \item \cbfa{Perimeter Scholars International - Students’ Training Accelerator for Research in Theory (PSI-START) Program} \textit{(10 week online school)} \\
    \cita{Perimeter Institute} \hfill{(May 24 - July 28, 2022)} \\
    \cita{University of Waterloo}
    
    \item \cbfc{Summer Particle Astrophysics Workshop} — \textit{(Virtual Attendee)} \\
    \cita{McDonald Institute for Astroparticle Physics} \hfill{(3 May - 12 May, 2022)}
    
    \item \cbfc{International Summer School on The Interstellar Medium of Galaxies, from the Epoch of Reionization to the Milky Way (ISM)} — \textit{(Virtual Attendee)} \\
    \cita{ISM Galaxies 2021} \hfill{(12 July - 23 July, 2021)}
    
    \item \cbfc{Introductory Summer School in Astronomy and Astrophysics (ISSAA)} — \textit{(Virtual Attendee)} \\
    \cita{Inter University Center for Astronomy and Astrophysics (IUCAA)} \hfill{(10 May - June 11, 2021)}
    
    \item \cbfc{Elements of Quantum Information Workshop} — \textit{(Virtual Attendee)} \\
    \cita{Christ Church College, Kanpur} \hfill{(12 March - 14 March 2021)}
    
\end{itemize}



%%%---------------------Co-Curricular Activities---------------------%%%
\section{{\faInstitution} Co-Curricular Activities}

\begin{itemize}
    \item \cbfc{Infinity} \\
    \cita{Ramnarain Ruia Autonomous College} \\
    Fest of Physics Department. \\
    
    \begin{itemize}
    
        \item \cita{Project Team} \hfill{(2 January, 2020 - 3 January, 2020)} \\
        \cbfd{Project:} Piezoelectric Generator.
        
        \item \cita{Project Team} \hfill{(4 January, 2019 - 5 January, 2019)} \\
        \cbfd{Project:} Bluetooth controlled Arduino Car.
        
        \item \cita{Arts Team} \hfill{(5 January, 2018 - 6 January, 2018)}

    \end{itemize}

\end{itemize}



%%%---------------------Rejected---------------------%%%
\section{{\faTags} Rejected}

\begin{itemize}

    \item \cbfd{Perimeter Scholars International - Students’ Training Accelerator for Research in Theory (PSI-START) Bridge Program } \\
    \cita{Perimeter Institute} \hfill{(2022)} \\
    \cita{University of Waterloo}
    
    \item \cbfd{Perimeter Scholars International (PSI) Program} \\
    \cita{University of Waterloo, Perimeter Institute} \hfill{(2022)}
    
\end{itemize}



\end{rightcolumn}



\end{paracol}
%---------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%  CV Ends Here  %%%%%%%%%%%%%%%%%%%%%
\end{document}
